Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\bf Fundamental Data Structures.} The {\em interval tree} \cite{bcko08} stores a set $S$ of intervals in $\real$ using $O(|S|)$ space such that, given any real value $q$, the intervals of $S$ containing $q$ can be found in $O(\log |S| + K)$ time, where $K$ is the number of intervals reported. It can also be used to detect whether $S$ has at least one interval containing $q$ in $O(\log |S|)$ time. The structure supports an insertion or deletion on $S$ in $O(\log |S|)$ time.

@@

Now, let us assume that each interval of $S$ is associated with a real-valued {\em weight}. Given a real value $q$, a {\em stabbing max} query returns the maximum weight of all the intervals in $S$ covering $q$ (if no such intervals exist, the query returns $-\infty$). We can store $S$ in a structure of \cite{aak+12} using $O(|S|)$ space that can answer such a query in $O(\log |S|)$ time. The structure supports an insertion or deletion on $S$ in $O(\log |S|)$ amortized time.

@@

The {\em priority search tree} (PST) \cite{m85} stores a set $P$ of points using $O(|P|)$ space such that, given a 3-sided rectangle $q = [x_1, x_2] \times [y, \infty)$, the points of $S$ covered by $q$ can be found in $O(\log |P| + K)$ time, where $K$ is the number of points reported. The structure supports an insertion or deletion on $S$ in $O(\log |S|)$ time.

>>>>

\extraspacing {\bf Fundamental Data Structures.} The {\em interval tree} \cite{bcko08} stores a set $S$ of intervals in $\real$ using $O(|S|)$ space such that, given any real value $q$, the intervals of $S$ containing $q$ can be found in $O(\log |S| + K)$ time, where $K$ is the number of intervals reported. It can also be used to detect whether $S$ has at least one interval containing $q$ in $O(\log |S|)$ time. The structure supports insertions and deletions on $S$ in $O(\log |S|)$ time.

@@

Now, let us assume that each interval of $S$ is associated with a real-valued {\em weight}. Given a real value $q$, a {\em stabbing max} query returns the maximum weight of all the intervals in $S$ covering $q$ (if no such intervals exist, the query returns $-\infty$). We can store $S$ in a structure of \cite{aak+12} using $O(|S|)$ space that can answer such a query in $O(\log |S|)$ time. The structure supports insertions and deletions on $S$ in $O(\log |S|)$ amortized time.

@@

The {\em priority search tree} (PST) \cite{m85} stores a set $P$ of points using $O(|P|)$ space such that, given a 3-sided rectangle $q = [x_1, x_2] \times [y, \infty)$, the points of $S$ covered by $q$ can be found in $O(\log |P| + K)$ time, where $K$ is the number of points reported. The structure supports insertions and deletions on $S$ in $O(\log |S|)$ time.
